Effects of pre-existing structures on the seismicity of the Charlevoix Seismic Zone

### 2019-06-30 Rebuttal_Letter.tex

\begin{response}{I recommend the authors to justify the assumption of the independency effect of involved factors on stress perturbations, or that they have consistently monotonous effects.}
    If the term, ``the independency effect of involved factors'', means the effects of independently controlled parameters on model results. The independency is never assumed and only a logical outcome from our experiment design, in which a reference model is compared with a model with only one parameter changed.

As for the monotonicity of model responses to varied parameters, our original results are already showing that that the controlled parameters have consistently monotonous effects. However, in this revision, we have run more models so that all the explored parameters have more regular intervals and thus the monotonicity of model responses can be exposed more clearly. For more details about the changes we have made in this regard, please refer to our response right below as well as those to the reviewer's specific comments.
\end{response}

\begin{response}{Also, I would be curious to know the sensitivity of your model to these factors, so that we will have a rough idea of the model resolution. It will also support your choice of parameter intervals, for example, moduli ratio and $\mu$ (Table 1). Thus, I suggest a moderate revision.}

    We have addressed this concern by running new models, making parameter intervals more regular. The expanded set of models not only provide the sensitivity information but also confirm that the model responses are monotonous to the control parameters in the considered ranges of values. Furthermore, the revised manuscript includes an updated justification for the choice of model parameters such as friction coefficient and elastic moduli ratio (Lines 377-383 and 431-434) as well as  in the supplementary information (Figs. S3-6) 
    %\note[EC]{Seun, specify where in the revised manuscript to look at for this information.} %\note[EC]{Why S5 is not listed?}
\end{response}

@@

  We have added the computational efficiency of our model in the model geometry section (Lines 131-137) of the manuscript. We did not add the computational efficiency to Table 1 because it does not change significantly among the models except for the SD65R25 model, which took about twice longer to run for the same model time. We do not clearly understand why this model is particularly slow but further analyzing computational efficiency is beyond the scope of this paper.

  %\add[EC]{, which took about twice longer to run for the same model time.} \annote[EC]{which may be due to the shallower fault dips.}{The shallower fault dips are the difference of SD65R25 from the others but does not directly explain why this model should take much less time. We can go ahead and speculate about possible reasons but it would be just enough to say that we do not clearly understand why this model is particularly slow and further analyzing computational efficiency is beyond the scope of this paper.}
  %\annote[EC]{except for the SD65R25 model}{This model then needs further explanation why it took a significantly longer or short time}. 
  %\note[EC]{Is there a reason why you did not follow the reviewer's suggestion to add this into to Table 1?}
\end{response}

\begin{response}{3. Line 131-133: I do not understand why you set your boundary conditions as the differential stress reaches 706 MPa. Do you set a criterion for shear stress somewhere else? Please make it more clear.}

  %\annote[EC]{We agree with the reviewer}{Agree only when you are sure that doing so would not negatively affect your arguments, assumptions or the overall integrity of your paper. Never confess; only justify.} on the high differential stress at seismogenic depth in our study, due to}
  The differential stress of 706 MPa at 10 km depth is based on Byerlee's law under the assumption of  
  %$\mu$ equal to 0.6 and \add[OF]{The equation of Byerlee's law has a μ value of 0.6. It is not an assumption in our study.}
  %\add[EC]{$\mu$ equal to 0.6 and} 
  the absence of pore-fluid pressure. The full derivation of this value is now provided in the supplementary information. Shear stress was not considered as a stopping criterion. In addition, we have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 538-549).

@@

    We have explored non-zero values of cohesion and their impact on the results are shown in Fig. S4 in the supplementary information. However, since low-cohesion results show a better spatial correlation with seismicity, the revised manuscript still presents models with zero cohesion as the main results.

\end{response}

\begin{response}{7. Line 226-231: When evaluate the modeling result, I suggest the authors to quantify the fitting between the simulated stress change and the earthquake hypocenters. It will help convincing the readers of preferred model parameters. For example, I do not see it necessarily to prefer the frictional coefficient equals to 0.3 over 0.4 based on Figure 11.}

   We have added a quantitative assessment of the correlation between the change in differential stress and the observed seismicity by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\% without accounting for uncertainty in hypocenter relocation (Line 209-213). This metric is now used for describing the model results and comparing different models throughout the revised manuscript. We also added a discussion on the choice of the friction coefficient in Lines 512-518.
    %: 1) the change in differential stress maps changes with fault geometry, and we have established an along-strike variation in the fault dips in this study; and 2) the 3D velocity model is very well defined in the upper 5 km depth which may introduced an uncertainty in the hypocenter relocation.
\end{response}

@@

\begin{response}{I think that Charlevoix is considered a meteor impact structure more than a crater. Although the difference is sometimes nebulous between the two, I would prefer if the authors referred to the impact structure. Another word that could be used is astrobleme ("star wound"). There are some interesting links that explain the difference.}

  We have changed the words "impact crater" and "crater" to "impact structure" throughout the manuscript.
\end{response}

\begin{response}{An aspect that may have been missed is the fact that the epicentral map, such as Fig. 1, does not show a complete view of the regional seismicity. The SSW portion of the St. Lawrence River (upstream towards Quebec City) is also active (although not as much as the interior of the astrobleme). The dataset shown is the one of Powell and Lamontagne (2017) which was a selection of events based on their locations within the network of seismograph stations, but for this map view, I suggest that a more complete dataset is presented. The data can be downloaded from the earthquakescanada web site.}

  We have plotted the complete dataset in Fig. 1. We represented the relocated hypocenters of Powell and Lamontagne (2017) as circles and the other earthquakes that are not in the relocated catalog as stars.
\end{response}

@@

\begin{response}{In a couple of places, authors use the expression 'large magnitude earthquakes'... Except for the 1925 M 6.2 earthquake, we are uncertain about the exact position of the 'large' earthquakes in Charlevoix (four other M6+; 1663; 1791, 1860,1870... although 1870 M 6.5 was probably near Ile-aux-Coudres). It would be better to say that the M4+ earthquakes, appear to occur more often in the NE portion of the CSZ. Stevens (1980) also found that some M4+ earthquakes of the period 1924-1980 also occurred at the SE end.}

  We have edited the manuscript accordingly (see Lines 458-460). We have also included the findings of Steven (1980) in our discussion.
\end{response}

@@

\begin{response}{The authors write that the focal mechanisms of the CSZ were not well defined. I disagree with them. You can check this OF report, which shows that the Quality 'A' mechanisms were well defined by the P first motions. I think that Mazzotti used most of them in his catalog.
https://geoscan.nrcan.gc.ca/starweb/geoscan/servlet.starweb?
path=geoscan/downloade.web\&search1=R=209378}

 The focal mechanisms are well defined, and we suggest that the focal mechanisms can be further constrained using waveform modeling to validate the magnitude of the stress rotation (Lines 572-575).
\end{response}

@@

\begin{response}{The model assumes an absence of pore-fluid pressure along faults. For this reason, the stress difference used by the authors is very high at seismogenic depth. It is my impression that worldwide, direct measurements and modelling of tectonic stresses suggest that the maximum crustal stress difference has an upper limit of about 100-200 MPa... very different from the 706 MPa suggested by the authors.
I think that the authors should discuss the possibility that high pore-fluid pressures exist at depth and their possible consequences. One aspect would be that faults could be reactivated at smaller angles from the maximum compressive stress and that the stress difference would have more realistic values.}

  The differential stress of 706MPa at 10 km depth is due to the assumption of the absence of pore-fluid pressure. The higher stopping criterion in our study is necessary to make faults slip at seismogenic depth under the assumption. We have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 538-549).
\end{response}

### 2019-06-30 Supporting_Information.tex
Addressed comments and changed figure background from transp to white.

\noindent\textbf{Stopping criterion of differential stress at 10 km depth}
\vspace{10mm} %5mm vertical space

@@

Based on Byerlee's law, $\tau$  = 50 MPa + 0.6$\,\sigma_n$, under the assumption of absence of pore-fluid pressure along the rift faults, $\tan \alpha = 0.6$, hence, $\sin \alpha = 0.5145$. $\sigma_{3}$ corresponds to the lithostatic stress amounting to 250.0 MPa at 10 km depth \add[EC]{for a density of XXXX kg/m$^{3}$}. With these values and the above expression, we get $\sigma_{1}$ = \annote[EC]{956.5}{Pay attention to the number of significant figures! I don't think our calculations can afford 7 or 8-digit precision so I rounded off the original value leaving 4 digits.} MPa. The differential stress at 10 km depth with no pore-fluid pressure, defined as $\sigma_{D} = \sigma_{1} - \sigma_{3})$, is 706.5 MPa.

@@

\note[EC]{Turn the first long phrase into a sentence. Right now it reads like a figure caption but it shouldn't in a normal paragraph.} The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) for models with different impact structure-crust density ratio (Fig. \ref{S3}).  The maps show no significant change with density ratio. In this study, we choose the density ratio of 10\% to represent damaged crustal rock. 
\vspace{10mm} %5mm vertical space

\begin{figure}[ht]
\setfigurenum{S3}
\includegraphics[width=25pc]{Figures/effect_of_density.png}
\caption{\note[EC]{Symbol descriptions are missing. Include those in Fig. S4 caption.} Effect of impact structure-crust density ratio on the $\Delta\sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ at 10 km depth. Earthquakes within 2 km of each depth slice are represented by black dots in \ref{S3}A. The outline of the impact structure is represented as black circle. Each figure is 70 $\times$ 70 km.}
\label{S3}
\end{figure}

@@

\note[EC]{Turn the first long phrase into a sentence. Right now it reads like a figure caption but it shouldn't in a normal paragraph.} The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) at various depths from the SD70R100 model (Fig. \ref{S4}).  $\Delta\sigma_{D}^{\prime}$ shows increased $\sigma_{D}$ relative to SNFR25 throughout the entire length of the rift faults at and below 15 km depth, hence the model predicts earthquakes in those regions.

@@

We run 4 models in total to assess the effects of impact structure-to-crust moduli ratio assuming that the impact structure was softened. The ratio equal to 1, for instance, means that the impact structure was not softened and thus has the elastic moduli with those of the surrounding crust. The models show a better spatial correlation with the observed seismicity when the moduli ratio is 0.25.

@@

Magnitudes of $\Delta\sigma_D^{\prime}$ and \annote[EC]{$\phi_{\max}$}{Fig. S6B doesn't support this.} decrease with increasing cohesion. $\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity for all the fault cohesions\annote[EC]{, especially well when the cohesion is less than 5 MPa}{What makes you say so? Can't you use the new metric for this argument?} (Fig. \ref{S6}A). However, the models could not explain a few earthquakes in the SW corner of the crater, where $\Delta\sigma_D^{\prime}$ is negative. The $\Delta\sigma_D^{\prime}$ is not affected by a change in cohesion between 0 and 5 MPa. However, $\phi_{\max}$ approaches the reference no-fault model as the cohesion increases (Fig. \ref{S6}B). As cohesion increases, $\Delta\phi_{\max}$ decreases in value and the rotation is concentrated in the fault region outside the crater (Fig. \ref{S6}C). $\Delta\phi_{\max}$ is up to 10.8$^\circ$ when the cohesion is less than 5 MPa.

\note[EC]{Why do you make remarks on $\mu$ mentioning cohesion only little in the paragraph for the effects of cohesion?} Figure \ref{S6} suggests that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope. We present models with zero cohesion in the main text because to explain the spatial distribution of observed seismicity in the CSZ.

\begin{figure}[ht]
\setfigurenum{S6}
\includegraphics[width=25pc]{Figures/SD70R25C_S2.png}
\caption{Same as \ref{S3} but for the models with different cohesion values.}
\label{S6}
\end{figure}

\pagebreak

>>>>

\noindent\textbf{Stopping criterion of differential stress at 10 km depth}
%\vspace{10mm} %5mm vertical space

@@

Based on Byerlee's law, $\tau$  = 50 MPa + 0.6$\,\sigma_n$, under the assumption of absence of pore-fluid pressure along the rift faults, $\tan \alpha = 0.6$, hence, $\sin \alpha = 0.5145$. $\sigma_{3}$ corresponds to the lithostatic stress amounting to 250.0 MPa at 10 km depth for a density of 2.55 kg/m$^{3}$.
%\add[EC]{for a density of XXXX kg/m$^{3}$}. 
With these values and the above expression, we get $\sigma_{1}$ = 956.5 MPa.
%\annote[EC]{956.5}{Pay attention to the number of significant figures! I don't think our calculations can afford 7 or 8-digit precision so I rounded off the original value leaving 4 digits.} MPa. 
The differential stress at 10 km depth with no pore-fluid pressure, defined as $\sigma_{D} = \sigma_{1} - \sigma_{3}$, is 706.5 MPa.

@@

%\note[EC]{Turn the first long phrase into a sentence. Right now it reads like a figure caption but it shouldn't in a normal paragraph.} The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) for models with different impact structure-crust density ratio (Fig. \ref{S3}).

We explore the effects of density reduction from 0 to 20 \% in a series of models in which the rift faults dip at 70$^{\circ}$ (i.e., SD70R25) (Fig. \ref{S3}). No significant changes in the model results were found in these models. In this study, we choose the density ratio of 10\% to represent damaged crustal rock. 
\vspace{10mm} %5mm vertical space

\begin{figure}[ht]
\setfigurenum{S3}
\includegraphics[width=25pc]{Figures/effect_of_density.png}
\caption{
%\note[EC]{Symbol descriptions are missing. Include those in Fig. S4 caption.} 
Effect of impact structure-crust density ratio on the percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$) and the change in $\phi_{\max}$ ($\Delta \phi_{\max}^{\prime}$) at 10 km depth. Earthquakes within 2 km of each depth slice are represented by black dots in \ref{S3}A. The outline of the impact structure is represented as black circle. Each figure is 70 $\times$ 70 km.}
\label{S3}
\end{figure}

@@

We compute $\Delta \sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ in the SD70R100 model (Fig. \ref{S4}). The model exhibit the effects of the rift faults since the impact structure and the crust have the same elastic moduli. 
%\note[EC]{Turn the first long phrase into a sentence. Right now it reads like a figure caption but it shouldn't in a normal paragraph.} The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) at various depths from the SD70R100 model (Fig. \ref{S4}).  
$\Delta\sigma_{D}^{\prime}$ shows increased $\sigma_{D}$ relative to SNFR25 throughout the entire length of the rift faults at and below 15 km depth, hence the model predicts earthquakes in those regions.

@@

We run 4 models in total to assess the effects of impact structure-to-crust moduli ratio assuming that the impact structure was softened (Fig. \ref{S5}). The ratio equal to 1, for instance, means that the impact structure was not softened and thus has the elastic moduli with those of the surrounding crust. The models show a better spatial correlation with the observed seismicity when the moduli ratio is 0.25.

@@

%\vspace{10mm} %5mm vertical space

\begin{figure}[ht]
\setfigurenum{S6}
\includegraphics[width=25pc]{Figures/SD70R25C_S6.png}
\caption{Same as \ref{S3} but for the models with different cohesion values.}
\label{S6}
\end{figure}

%\vspace{10mm} %5mm vertical space

Magnitudes of $\Delta\sigma_D^{\prime}$ % and \annote[EC]{$\phi_{\max}$}{Fig. S6B doesn't support this.} 
decrease with increasing cohesion. $\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity %for all the fault cohesions, especially well 
when the cohesion is less than 5 MPa with about 70\% of the hypocenters fall in the region with $\Delta\sigma_D^{\prime} \ge$ 0.5\% (Fig. \ref{S6}A). %The percentages of the hypocenters in the region with $\Delta\sigma_D^{\prime} \ge$ 0.5\% decrease to 61\% and 47\% for cohesion values of 20 and 30 MPa, respectively.
%\annote[EC]{, especially well when the cohesion is less than 5 MPa}{What makes you say so? Can't you use the new metric for this argument?} (Fig. \ref{S6}A). 
However, the models could not explain a few earthquakes in the SW corner of the crater, where $\Delta\sigma_D^{\prime}$ is negative. The $\Delta\sigma_D^{\prime}$ is not affected by a change in cohesion between 0 and 5 MPa. However, $\phi_{\max}$ approaches the reference no-fault model as the cohesion increases (Fig. \ref{S6}B). As cohesion increases, $\Delta\phi_{\max}$ decreases in value and the rotation is concentrated in the fault region outside the crater (Fig. \ref{S6}C). $\Delta\phi_{\max}$ is up to 10.8$^\circ$ when the cohesion is less than 5 MPa. We present models with zero cohesion in the main text to explain the spatial distribution of observed seismicity in the CSZ.

%\note[EC]{Why do you make remarks on $\mu$ mentioning cohesion only little in the paragraph for the effects of cohesion?} Figure \ref{S6} suggests that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope. We present models with zero cohesion in the main text because to explain the spatial distribution of observed seismicity in the CSZ.

%\pagebreak

### 2019-06-30 main_full_manuscript.tex
Addressed comments and changed figure background from transp to white.

%% To submit your paper:
\PassOptionsToPackage{inline}{trackchanges}
\documentclass[draft]{agujournal2018}
\usepackage{apacite}
\usepackage{comment}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\linenumbers
%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  \add[editor]{Text to add}
%  \remove[editor]{Text to remove}
%  \change[editor]{Text to remove}{Text to add}
%
% complete documentation is here: http://trackchanges.sourceforge.net/
\addeditor{EC}
\addeditor{OF}

@@

\begin{table}
\caption{List of numerical models} 
%\note[EC]{Each symbol needs a description. Cohesion needs a unit. I gave a try with the $\dagger$ symbol.}}
\centering
\begin{tabular}{llcccccc}
\hline
Model & Velocity Model & Dip of Rift Faults & Moduli ratio & $\mu^{\dagger}$ & $C^{\dagger}$ (MPa) & K$^{\dagger,*}$ (MPa) & G$^{\dagger,*}$ (MPa) \\
\hline
SNFR25  & Saguenay Region$^{1}$ & No faults & 0.25 & 0.3 & 0 & 55.7 & 32.7  \\
SD70R25  &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.3 & 0 & 55.7 & 32.7 \\
SD70R25V  &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1-0.6 & 0 & 55.7 & 32.7 \\
%SD70R25M1 &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1 & 0 \\
SD65R25  &  & $65^\circ-40^\circ-40^\circ$  & 0.25 & 0.3 & 0 & 55.7 & 32.7\\
SD70R50  &  & $70^\circ-70^\circ-70^\circ$  & 0.5 & 0.3 & 0 & 55.7 & 32.7 \\
SD70R100   &  & $70^\circ-70^\circ-70^\circ$  & 1.0 & 0.3 & 0 & 55.7 & 32.7 \\
LD70R25 & 1-D Model$^{2}$ & $70^\circ-70^\circ-70^\circ$ & 0.25 & 0.3  & 0 & 60.0 & 35.7 \\
TD70 & Tomography$^{3}$ & $70^\circ-70^\circ-70^\circ$ & - & 0.3 & 0 & 58.7 & 35.3 \\
\hline
\multicolumn{8}{l}{$^{1}$\citet{Somerville1990}. $^{2}$\citet{lamontagne1999}. $^{3}$\citet{Powell_2017}.$^{*}$K, G at 10 km depth.} \\
\multicolumn{8}{l}{$^{\dagger}$$\mu$, $C$, $K$ and $G$ are friction coefficient, cohesion, bulk and shear modulus, respectively.}

@@

\subsection{Frictional strengths of the rift faults}
The surface expression of the rift faults used in this study correspond to the Gouffre Northwest Fault, Saint-Laurent fault and Charlevoix Fault (Fig. 1). We did not consider the South Shore fault given its aseismic nature \change[OF]{and its location at the extreme eastern edge of the crater}{, although it appears to mark a boundary to the active zone}~\citep{lamontagne1999}. Our models show that a $\mu$ of 0.3 and cohesion values of 0 MPa create $\Delta\sigma_{D}^\prime$ maps that spatially correlate with the seismicity of CSZ and the observed stress rotations (Fig. \ref{fig:eff_of_mu}). \add[OF]{We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig. S6). Cohesion values less than 5 MPa could better explain the spatial distribution of observed seismicity in the CSZ than the greater values.} \add[OF]{$\mu$ equal to 0.4 also seems suitable to the rift faults as the $\Delta\sigma_{D}^\prime$ maps spatially correlate well with the seismicity of the CSZ. A small number of earthquakes also occurred at the SW region outside the impact structure (Fig. $\ref{figone}$), however, previous studies in the CSZ agreed with a finite extent of the seismicity}~\citep[e.g.,][]{Stevens1980}. \note[EC]{I don't understand the point of the sentence about the finite extent of the seismicity. Is it necessary?}
\change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig. \ref{figone}). \note[EC]{This sentence should be in the model setup unless you want to discuss implications of this difference.}

@@

Our models can only explain about 50\% of the observed $SH_{\max}$ rotation. A possible hypothesis for the remaining stress rotation is a change in the dip of the rift faults with depth and the effect of postglacial rebound. \remove[OF]{The high stress rotation could also be due to unconstrained focal mechanisms used in the stress inversion.} Most of the focal mechanisms used for stress inversion \add[OF]{in the CSZ} are obtained from first motion P and SH waves~\citep{Mazzotti_2010,lamontagne1998}. \change[OF]{Better constrained}{The} focal mechanisms \note[EC]{What do you mean by ``focal mechanisms are `good\rq{}''? It would be good/nice to have better constrained ones, you mean?}\add[OF]{are good, and we suggest that the focal mechanisms can be further constrained} using waveform modeling \remove[OF]{will be needed} to validate the magnitude of the stress rotation.

>>>>

%% To submit your paper:
\PassOptionsToPackage{inline}{trackchanges}
\documentclass[draft]{agujournal2018}
\usepackage{apacite} 
\bibliographystyle{apacite}

\usepackage{comment}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\linenumbers
%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  \add[editor]{Text to add}
%  \remove[editor]{Text to remove}
%  \change[editor]{Text to remove}{Text to add}
%
% complete documentation is here: http://trackchanges.sourceforge.net/
\addeditor{EC}
\addeditor{OF}

@@

\begin{table}
\caption{List of numerical models} 
%\note[EC]{Each symbol needs a description. Cohesion needs a unit. I gave a try with the $\dagger$ symbol.}}
\centering
\begin{tabular}{llcccccc}
\hline
Model & Velocity Model & Dip of Rift Faults & Moduli ratio & $\mu^{\dagger}$ & $C^{\dagger}$ (MPa) & K$^{\dagger,*}$ (MPa) & G$^{\dagger,*}$ (MPa) \\
\hline
SNFR25  & Saguenay Region$^{1}$ & No faults & 0.25 & 0.3 & 0 & 55.7 & 32.7  \\
SD70R25  &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.3 & 0 & 55.7 & 32.7 \\
SD70R25V  &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1-0.6 & 0 & 55.7 & 32.7 \\
%SD70R25M1 &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1 & 0 \\
SD65R25  &  & $65^\circ-40^\circ-40^\circ$  & 0.25 & 0.3 & 0 & 55.7 & 32.7\\
SD70R50  &  & $70^\circ-70^\circ-70^\circ$  & 0.5 & 0.3 & 0 & 55.7 & 32.7 \\
SD70R100   &  & $70^\circ-70^\circ-70^\circ$  & 1.0 & 0.3 & 0 & 55.7 & 32.7 \\
LD70R25 & 1-D Model$^{2}$ & $70^\circ-70^\circ-70^\circ$ & 0.25 & 0.3  & 0 & 60.0 & 35.7 \\
TD70 & Tomography$^{3}$ & $70^\circ-70^\circ-70^\circ$ & - & 0.3 & 0 & 58.7 & 35.3 \\
\hline
\multicolumn{8}{l}{$^{1}$\citet{Somerville1990}. $^{2}$\citet{lamontagne1999}. $^{3}$\citet{Powell_2017}. $^{*}$K, G at 10 km depth.} \\
\multicolumn{8}{l}{$^{\dagger}$$\mu$, $C$, $K$ and $G$ are friction coefficient, cohesion, bulk and shear modulus, respectively.}

@@

\subsection{Frictional strengths of the rift faults}
The surface expression of the rift faults used in this study correspond to the Gouffre Northwest Fault, Saint-Laurent fault and Charlevoix Fault (Fig. 1). We did not consider the South Shore fault given its aseismic nature \change[OF]{and its location at the extreme eastern edge of the crater}{, although it appears to mark a boundary to the active zone}~\citep{lamontagne1999}. Our models show that a $\mu$ of 0.3 and cohesion values of 0 MPa create $\Delta\sigma_{D}^\prime$ maps that spatially correlate with the seismicity of CSZ and the observed stress rotations (Fig. \ref{fig:eff_of_mu}). \add[OF]{We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig. S6). Cohesion values less than 5 MPa could better explain the spatial distribution of observed seismicity in the CSZ than the greater values.} \add[OF]{$\mu$ equal to 0.4 also seems suitable to the rift faults as the $\Delta\sigma_{D}^\prime$ maps spatially correlate well with the seismicity of the CSZ. A small number of earthquakes also occurred at the SW region outside the impact structure (Fig. $\ref{figone}$)}.
%, however, previous studies in the CSZ agreed with a finite extent of the seismicity}~\citep[e.g.,][]{Stevens1980}. \note[EC]{I don't understand the point of the sentence about the finite extent of the seismicity. Is it necessary?}\change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig. \ref{figone}). \note[EC]{This sentence should be in the model setup unless you want to discuss implications of this difference.}

@@

Our models can only explain about 50\% of the observed $SH_{\max}$ rotation. A possible hypothesis for the remaining stress rotation is a change in the dip of the rift faults with depth and the effect of postglacial rebound. \remove[OF]{The high stress rotation could also be due to unconstrained focal mechanisms used in the stress inversion.} Most of the focal mechanisms used for stress inversion \add[OF]{in the CSZ} are obtained from first motion P and SH waves~\citep{Mazzotti_2010,lamontagne1998}. \change[OF]{Better constrained}{The} focal mechanisms %\note[EC]{What do you mean by ``focal mechanisms are `good\rq{}''? It would be good/nice to have better constrained ones, you mean?}
\add[OF]{are well defined, and we suggest that the focal mechanisms can be further constrained} using waveform modeling \remove[OF]{will be needed} to validate the magnitude of the stress rotation.
